Beyond ``Horizontal'' and ``Vertical'':\\ The Welfare Effects of Complex Integration

### 2022-02-10 presentations/FTC/BargainingSimsSlides.tex
added data for trash sims

\addtobeamertemplate{title page}{\footnotesize The views expressed herein are entirely those of the authors and should not be purported to reflect those of the U.S. Department of Justice.}{}
\beamertemplatenavigationsymbolsempty
%\beamerdefaultoverlayspecification{<+->}

@@

\begin{itemize}
  \item Assume firms set prices simultaneously in Bertrand Nash equilibrium
  \item Retailer \textcolor{cyan}{constant}  marginal cost consists of wholesale fee $p^W_{rw}$ and other costs $c^R_{rw}$
  \item Profit function for retailer $r$ is
  \begin{equation*}
  \pi^r = \sum_{w \in \mathbb{W}^r} [p_{rw} - p^W_{rw} - c^R_{rw}] s_{rw} M
  \end{equation*}
  \item Resulting first order conditions determine downstream equilibrium prices
  \begin{equation*}
  \sum_{x \in \mathbb{W}^r} [p_{rx} - p^W_{rx} - c^R_{rx}] \frac{\partial s_{rx}}{\partial p_{rw}} + s_{rw} = 0
  \end{equation*}
\end{itemize}

@@

\begin{itemize}
  \item Assume a \textcolor{cyan}{linear} wholesale price set by Nash Bargaining
  \begin{equation*}
  \max_{p^W_{rw}} (\pi^r - d^r (\mathbb{W}^r \setminus \{w\}))^{\lambda_{rw}} (\pi^w - d^w (\mathbb{R}^w \setminus \{r\}
  ))^{1 - \lambda_{rw}}
  \end{equation*}
  \item $\{\lambda_{rw}; \forall r \in \mathbb{R}, \forall w \in \mathbb{W}\}$ are parameters to be calibrated
  \item Wholesaler marginal costs  are \textcolor{cyan}{constant} and equal $c^W_{rw}$
  \item Profit function for wholesaler $w$ is
  \begin{equation*}
  \pi^w = \sum_{r \in \mathbb{R}^w} [p^W_{rw} - c^W_{rw}] s_{rw} M
  \end{equation*}
  \item All wholesalers and retailers reach an agreement in equilibrium.
\end{itemize}

>>>>

\addtobeamertemplate{title page}{\footnotesize The views expressed herein are entirely those of the authors and should not be purported to reflect those of the Board of Governors, Federal Trade Commission, or U.S. Department of Justice.}{}
\beamertemplatenavigationsymbolsempty
%\beamerdefaultoverlayspecification{<+->}

@@

\begin{itemize}
  \item Assume firms set prices simultaneously in Bertrand Nash equilibrium
  \item Retailer  marginal cost consists of wholesale fee $p^W_{rw}$ and other  \textcolor{cyan}{constant/linear} costs $c^R_{rw}$
  \item Profit function for retailer $r$ is
  \begin{equation*}
  \pi^r = \sum_{w \in \mathbb{W}^r} [p_{rw} - p^W_{rw} - c^R_{rw}] s_{rw} M
  \end{equation*}
  \item Resulting first order conditions determine downstream equilibrium prices
  \begin{equation*}
  \sum_{x \in \mathbb{W}^r} [p_{rx} - p^W_{rx} - c^R_{rx}] \frac{\partial s_{rx}}{\partial p_{rw}} + s_{rw} = 0
  \end{equation*}
\end{itemize}

@@

\begin{itemize}
  \item Assume a \textcolor{cyan}{linear} wholesale price set by Nash Bargaining
  \begin{equation*}
  \max_{p^W_{rw}} (\pi^r - d^r (\mathbb{W}^r \setminus \{w\}))^{\lambda_{rw}} (\pi^w - d^w (\mathbb{R}^w \setminus \{r\}
  ))^{1 - \lambda_{rw}}
  \end{equation*}
  \item $\{\lambda_{rw}; \forall r \in \mathbb{R}, \forall w \in \mathbb{W}\}$ are parameters to be calibrated
  \item Wholesaler marginal costs  are \textcolor{cyan}{constant/linear} and equal $c^W_{rw}$
  \item Profit function for wholesaler $w$ is
  \begin{equation*}
  \pi^w = \sum_{r \in \mathbb{R}^w} [p^W_{rw} - c^W_{rw}] s_{rw} M
  \end{equation*}
  \item All wholesalers and retailers reach an agreement in equilibrium.
\end{itemize}
